Quality Metrics for SKOS Vocabularies

### 2012-03-14 background.tex
added some comments by antoine

% Argue why we need higher-level criteria

\todo{CM}{argue why quality criteria beyond integrity conditions are needed; provide some good arguments and refer to the literature. The focus of this paragraph should be on quality in the controlled vocabulary domain...}

@@

\begin{itemize}
    \item Existing literature
    \item Mailing list discussions
    \item \ldots \todo{cm}{think about and finish this paragraph and lists.}
\end{itemize}

>>>>

% Argue why we need higher-level criteria
With controlled vocabularies being available in the Web of Data, they are adopted for use-cases or domains not originally intended by the creators. These use-cases often have specific and overlapping requirements regarding, e.g., structure, availability or documentation of the underlying controlled vocabularies. To give some examples, loose concepts might negatively impact retrieval recall, missing entry points to an aggregated set of concepts impedes orientation for human users, and inconsistent relations hinder queries across distinct datsets. Thus there is a need for higher-level quality criteria that go beyond the integrity conditions given in the SKOS data model, which take into account characteristics of the intended application areas. \todo{CM}{provide references}

%\todo{CM}{argue why quality criteria beyond integrity conditions are needed; provide some good arguments and refer to the literature. %The focus of this paragraph should be on quality in the controlled vocabulary domain...}

@@

\begin{itemize}
    \item Existing literature
    \item Mailing list discussions
		\item Practices in current vocabulary development projects
		\item Review of online available vocabularies from different domains
    \item Feedback from experts in vocabulary creation
%\ldots \todo{cm}{think about and finish this paragraph and lists.}
\end{itemize}
